Local Group Satellite Alignments in a Cosmological Context

### 2017-07-05 paper/paper.tex
new plot

We build the LGP sample by keeping the pairs in the IP sample with
a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
and a relative radial velocity (including the Hubble flow) of $V_{AB}<-100$ km s$^{-1}$.
These intervals are close to the Local Group observed values.

>>>>

We build the LGP sample by keeping the pairs in the IP sample with
a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
and a negative relative radial velocity (including the Hubble flow) 
These intervals are close to the Local Group observed values.
The LGP sample is reduced to $12$ pairs.

Figure \ref{fig:samples} show the results for the IP and LGP samples
in the plane of radial velocity versus distance.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
\caption{Halo pair samples used in this paper located in the
  plane of relative radial velocity $V_{r,AB}$ versus 
  distance $R_{AB}$ between the two halos in the pair.
  The IP sample (24 pairs) is a general pair sample, while the LGP
  sample (12 pairs) resemples the separation and kinematic
  conditions observed in the Local Group.} 
\label{fig:samples}
\end{figure}
